---
title: "Single-case Design Evaluation"
author: "Shawn Gilroy"
date: "7/11/2022"
output:
  pdf_document: default
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE, fig.path = "plots/")

library(dplyr)   # included for infix logic
library(emmeans) # CI's
library(fxl)     # core plotting methods (MUST INSTALL FROM GITHUB, NOT CRAN)
library(lmtest)  # p values
library(nlme)    # core fitting libraries

data = read.csv("CASCD_Data_Clean.csv") %>%
  filter(!is.na(Latency))

```

## Descriptive Data

...

## Fits using Ordinary Least Squares (Piecewise Level/Trend)

```{r olsLT}
fit.ols = lm(Latency ~ Session + Phase + SC, data = data)

summary(fit.ols)

acf(residuals(fit.ols))
acf(residuals(fit.ols), type = "partial")
dwtest(fit.ols, alternative = "two.sided")

```

Note: Durbin-Watson test suggests that degree of autocorrelation in OLS residuals is non-trivial. 

## Fits using Generalized Least Squares (Piecewise Level/Trend)

```{r glsLT}

# Without random effects
fit.gls = gls(Latency ~ Session + Phase + SC,
              method = "ML",
              correlation = corARMA(p = 1),
              data = data)

# With random intercepts and slopes per participant
fit.lme = lme(Latency ~ Session + Phase + SC,
              data = data,
              method = "ML",
              correlation = corARMA(p = 1),
              random = ~ 1 + Phase + SC | Participant)

anova(fit.gls, fit.lme)

```

Note: across fits, the added complexity of the random effects isn't justified.

## Model Selection for Generalized Least Squares

```{r glsModelSelection1}

fit.gls2 = gls(Latency ~ Phase,
               method = "ML",
               correlation = corARMA(p = 1),
               data = data)

anova(fit.gls, fit.gls2)

```

Note: Trend factor not worth the cost

```{r glsModelSelection2}

fit.gls3 = gls(Latency ~ 1,
               method = "ML",
               correlation = corARMA(p = 1),
               data = data)

anova(fit.gls2, fit.gls3)

```

Note: Phase factor is significant

## Evaluating Autocorrelation Adjustments

```{r glsAutocorrelation}

fit.gls2.1 = fit.gls2
fit.gls2.2 = update(fit.gls2, correlation = corARMA(p = 2))
anova(fit.gls2.1, fit.gls2.2)

fit.gls2.3 = update(fit.gls2, correlation = corARMA(p = 3))
anova(fit.gls2.1, fit.gls2.3)

fit.gls2.4 = update(fit.gls2, correlation = corARMA(p = 4))
anova(fit.gls2.1, fit.gls2.4)

```

Note: No real improvement beyond a lag of 1

```{r fxlOutput, echo=FALSE}

data$pred = predict(fit.gls2)

output = summary(emmeans(fit.gls2, "Phase", data = data, type = "response"))

data[data$Phase == "BL","LCL"]  <- output$lower.CL[1]
data[data$Phase == "INT","LCL"] <- output$lower.CL[2]

data[data$Phase == "BL","UCL"]  <- output$upper.CL[1]
data[data$Phase == "INT","UCL"] <- output$upper.CL[2]

# Initial setup, sets core aesthetics (what data to show where)
scr_plot(data, aesthetics = list(x     = Session,
                                 y     = Latency,
                                 p     = Phase,
                                 facet = Participant),
         mai = c(0.375, 0.375, 0.1,  0.0),
         omi = c(0.25,  0.25,  0.25, 0.1)) %>%
  scr_xoverride(c(1, 35),
    xticks = c(1, 5, 10, 15, 20, 25, 30, 35)) %>%        # manually override x-axis (make extra room for labels)
  scr_yoverride(c(0, 700),           # manually override y-axis and tick interval (tick every 10 units)
                ydelta = 100) %>%
  scr_points(cex = 1.25) %>%            # plot points, using x/y from aesthetics
  scr_lines(size = 1) %>%            # plot lines, using x/y from aesthetics
  scr_lines(size = 1,
            mapping = list(x = Session,
                           y = pred,
                           p = Phase),
            color = "red") %>%
  scr_lines(size = 1,
            mapping = list(x = Session,
                           y = LCL,
                           p = Phase),
            lty = 2,
            color = "gray") %>%
  scr_lines(size = 1,
            mapping = list(x = Session,
                           y = UCL,
                           p = Phase),
            lty = 2,
            color = "gray") %>%
  scr_label_phase(facet  = "1",  # plot labels on specific facet
                  cex    = 1,
                  adj    = 0,
                  y      = 700,
                  labels = list(     # list of labels to draw (will use assigned key for label)
                    "Baseline"       = list(x = 1),
                    "Treatment"      = list(x = 13))) %>%
  scr_label_facet(cex    = 1,         # plot labels across facets (not within a single facet)
                  adj    = 1,
                  y      = 750,
                  labels = list(     # list of labels to draw (will use assigned key for label)
                    "1" = list(x = 36, label = "Participant 1"),
                    "2" = list(x = 36, label = "Participant 2"),
                    "3" = list(x = 36, label = "Participant 3"),
                    "4" = list(x = 36, label = "Participant 4"))) %>%
  scr_plines_mbd(lines = list(       # plot linked phase lines (note: drawn from top through bottom)
    "A" = list(                      # list of phase lines to draw (where to draw lines across each participant)
      "1"  = list(x1 = 11.5,
                  y1 = 700),
      "2"  = list(x1 = 19.5,
                  y1 = 700),
      "3"  = list(x1 = 23.5,
                  y1 = 700),
      "4"  = list(x1 = 26.5,
                  y1 = 700)
    )
  )) %>%
  scr_xlabel("Session") %>%          # Override x-axis label (bottom only shown by default)
  scr_ylabel("Latency") # Override y-axis label (centered, leftmost label)

```

## Interpretation of Fixed Effects

```{r fitResults}

summary(fit.gls2)

```

On the overall, the latency observed across individuals decreased as a function of 82.81102 units following intervention.
